Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-21 4_methodology/methodology.tex
Shortening - in progress

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. Considering the fact that the process models may not be defined beforehand or outdated to reflect latest state of the process, they are mined from event logs. However, if there are process models that represent the event logs, this stage can be skipped. In order to mine process models, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs. Black-box of this stage is illustrated in Figure~\ref{fig:process-model-mining-blackbox} and this stage is called for every organization's event logs to create their own process models in Workflow net formalization.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/process-model-mining-blackbox}
  \caption{Process Model Mining Stage as Black-box }
  \label{fig:process-model-mining-blackbox}
\end{figure}

@@

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed. This approach is formalized in Algorithm~\ref{algo:recgen}.
 \begin{algorithm}
\DontPrintSemicolon % Some LaTeX compilers require you to use \dontprintsemicolon instead 
\KwIn{$O$ organization, $C$ Cluster Analysis Data, $P$ performance difference threshold}
\KwOut{$Recommendations$ a set of recommendations}
$Recommendations \leftarrow \{\}$ \;
$i \leftarrow C(Assignments(O))$ \;
\For{$Centroid \in C(Cluster Centroids_{i})$} { 
  \For{$Centroid' \in C(Cluster Centroids_{j})\ i\neq j$} { 
    \If{$Centroid(A_{start}) = Centroid'(A_{start})\ \&\ Centroid(A_{end}) = Centroid'(A_{end})$} {
      \If{ ($\left |  Centroid(Value) -  Centroid'(Value)\right | \div Centroid(Value)) \geq P$  } {
        $A_{start} \leftarrow Centroid(A_{start})$ \;
        $A_{end} \leftarrow Centroid(A_{end})$ \;
        $MismatchPatterns \leftarrow \{\}$ \;
        \For{$O' \in C(Assignments(j))$} {
          $MismatchPatterns$ \leftarrow  Mismatch Pattern Analysis($O$,$O'$,$A_{start}$,$A_{end}$) \;
        }
        $Recommendations$ \leftarrow  Recommendation($O$,$A_{start}$,$A_{end}$, $MismatchPatterns$) \;
      }
    }
  }
}
\Return{$Recommendations$} \;
\caption{Recommendation Generation}
\label{algo:recgen}
\end{algorithm}

This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

>>>>

\subsection{Process Model Mining}
\label{subsec:process-model-mining}
Process model mining in the proposed approach has the aim of creating reproducible and generalized process models from event logs. Considering the fact that the process models may not be defined beforehand or outdated to reflect latest state of the process, they are mined from event logs. However, if there are process models that represent the event logs, this stage can be skipped. In order to mine process models, implementation of the \textit{Inductive Miner Infrequent (IMi)}, which is proposed in \cite{leemans2014discoveringinfrequent} as an extension to \textit{Inductive Miner} to handle noise in the event logs, is used in this study. In order to set a filtering threshold, a user-provided value between 0 to 1 is added as input to the method in addition to event logs.

@@

Algorithm of recommendation generation function is based on the idea of checking other clusters for a significant change in performance indicators, where significance is defined by the threshold provided by user. After finding significant difference, all organizations in other clusters are checked against mismatch patterns with the starting and ending activities defined in performance indicators. Only mismatches which are located between the activities that causes high level of difference in performance indicators are analyzed. This approach is formalized in Algorithm~\ref{algo:recgen}.
 \begin{algorithm}
\DontPrintSemicolon % Some LaTeX compilers require you to use \dontprintsemicolon instead 
\KwIn{$O$ organization, $C$ Cluster Analysis Data, $P$ performance difference threshold}
\KwOut{$Recommendations$ a set of recommendations}
$Recommendations \leftarrow \{\}$ \;
$i \leftarrow C(Assignments(O))$ \;
\For{$Centroid \in C(Cluster Centroids_{i})$} { 
  \For{$Centroid' \in C(Cluster Centroids_{j})\ i\neq j$} { 
    \If{$Centroid(A_{start}) = Centroid'(A_{start})\ \&\ Centroid(A_{end}) = Centroid'(A_{end})$} {
      \If{ ($\left |  Centroid(Value) -  Centroid'(Value)\right | \div Centroid(Value)) \geq P$  } {
        $A_{start} \leftarrow Centroid(A_{start})$ \;
        $A_{end} \leftarrow Centroid(A_{end})$ \;
        $MismatchPatterns \leftarrow \{\}$ \;
        \For{$O' \in C(Assignments(j))$} {
          $MismatchPatterns$ \leftarrow  Mismatch Pattern Analysis($O$,$O'$,$A_{start}$,$A_{end}$) \;
        }
        $Recommendations$ \leftarrow  Recommendation($O$,$A_{start}$,$A_{end}$, $MismatchPatterns$) \;
      }
    }
  }
}
\Return{$Recommendations$} \;
\caption{Recommendation Generation}
\label{algo:recgen}
\end{algorithm}
This stage of methodology can be visualized as gathering inputs of mismatch patterns data and cluster analysis data in Figure~\ref{fig:recommendation-generation-blackox}.
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{4_methodology/recommendation-generation-blackbox}
  \caption{Recommendation Generation Stage as Black-box}
  \label{fig:recommendation-generation-blackox}
\end{figure}

### 2015-11-21 6_conclusion_future_work/conclusion_future_work.tex
Shortening - in progress

In this study, a new approach is proposed and tested for generating recommendations using cross-organizational process mining for process performance improvement. Cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used in an environment where processes are executed on several organizations. Results show that it is possible to use cross-organizational process mining and mismatch patterns for performance improvement recommendations. In this study, a four-stage solution is presented and their performances are explained. In addition, proposed methodology is developed as extensible and configurable set of plugins in ProM framework \cite{verbeek2010prom} and published as open-source. This makes the methodology open to include new process mining methods, mismatch patterns and clustering approaches as well as testing with different datasets.

>>>>

In this study, a new approach is proposed and tested for generating recommendations using cross-organizational process mining for process performance improvement. Cross-organizational process mining is applied with the idea of unsupervised learning where predictor variables related to performances of organizations are used in an environment where processes are executed on several organizations. Results show that it is possible to use cross-organizational process mining and mismatch patterns for performance improvement recommendations. In this study, proposed methodology is developed as extensible and configurable set of plugins in ProM framework \cite{verbeek2010prom} and published as open-source. This makes the methodology open to include new process mining methods, mismatch patterns and clustering approaches as well as testing with different datasets.
